Carbon Renaissance Whitepaper 1.0

### 2021-10-18 carbon_renaissance/template.tex
latest

 \href{https://orcid.org/0000-0000-0000-0000}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Greg Darragh}\\
	Carbon Renaissance\\
	\texttt{greg@crc.eco} \\
\And	
 \href{https://orcid.org/0000-0000-0000-0000}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Mick Viner-Smith}\\
	Carbon Renaissance\\
	\texttt{mick@crc.eco} \\	
\And
 \href{https://orcid.org/0000-0000-0000-0000}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Ian C. Moore, PhD}\\
	Syscoin Researcher\\
	\texttt{imoore@syscoin.org} \\
	\And
	\href{https://orcid.org/0000-0000-0000-0000}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Jagdeep Sidhu, MSc} \\
	Syscoin Core Developer\\
	Blockchain Foundry Inc.\\
	\texttt{jsidhu@blockchainfoundry.co} \\
}

@@

\hypersetup{
pdftitle={Stochastic Properties of EIP-1559 Basefees},
pdfsubject={q-bio.NC, q-bio.QM},
pdfauthor={Ian C. Moore, Jagdeep Sidhu},
pdfkeywords={Carbon Sequestration, Carbon Offsetting, Social Credit, NFT},
}

@@

We introduce a carbon offsetting program through the tokenization of work done (ie, via Green tokens) on a blockchain. We utilize Non-fungible tokens as IOU contracts to facilitate engagement between stakeholders interested in pollution prevention and those performing the carbon offsetting. To incentivize adoption, a Black reward token is offered for those who utilize the system, which can be staked to acquire  Green tokens introduced to the supply

@@

\keywords{Carbon Sequestration \and Carbon Offsetting  \and Social Credit \and NFT}

@@

We propose a Carbon offset design that creates natural economic incentives through business
processes on the blockchain tied to Non-fungible tokens (NFT) tokens issued from enterprise to participating companies which connect to Carbon offsetting processes. Upon audits of work, a fungible token (ie, Green token) is issued to companies involved based on a pre-negotiated ratio of tokens dispersed based on the quality of the work and quality of the credit-worthiness of the companies involved. Green tokens
represents auditing work done for carbon offsetting.

We conjecture that this will not only allow for incentives to modify spending behaviour of
consumers, but also produce a mechanism for stakeholders to adhere to carbon quotas by
purchasing and offsetting their carbon consumption through a novel token model. Furthermore, once our model is implemented for fair exchange of carbon tokens in auditable and censorship resistance mediums, we assert how this model can used to serve as a social credit component to a broader Universal Basic Income (UBI) model.

@@

Climate change is a well studied issue and is defined as global warming stemming from greenhouse gas emissions resulting from major shifts in weather patterns. As a result, it has recently garnered much attention on the world stage \cite{Kal96,Ten00,Hij05}. According to \cite{Glo21}, it is estimated that human activity accounts for 1.0 $^\circ$C of global warming above pre-industrial levels, and estimate that global warming is likely to reach 1.5$^\circ$C between 2030 and 2052. The EDGAR time series set shows that since the beginning of the 21$^{st}$ \cite{EDGAR19}, fossil CO$_{2}$ emissions have increased compared to the three previous decades; see Fig \ref{fig:edgars_co2_emissions}. It also shows that, as of 2018, global fossil CO$_{2}$ emissions have reached a total of 37.9 Gt CO$_{2}$. However, according to \cite{Liu20}, emissions have fallen \~ 1,900 MtCO$_{2}$ from 2019 to 2020 due mainly to the aviation and shipping sector due to the slowing of economic activity stemming from the 2020 pandemic. To combat this, carbon offsetting is the process by which many players are handling this issue.

\begin{figure}[h]
\centering
\includegraphics[width=5in]{edgars_co2_emissions.png}
\caption{Global Greenhouse Gas (GHG) emission per sector; see \cite{EDGAR19}. We can see the Power industry account for a large portion of global emissions, which provides insight as to where the largest opportunity for carbon reduction may be found.} 
\label{fig:edgars_co2_emissions}
\end{figure}

Carbon offsetting is done via sequestration which is the process where atmospheric carbon dioxide is captured and stored for the purpose of abating climate change. After carbon is captured, it goes mainly one of two ways: (a) permanently stored underground; or (b) converted into a carbon-containing product \cite{CBC19}. Currently, the market for corporate procurement for carbon removal is very undeveloped. However, there are a number of organizations that have made strides to address this issue; which include Amazon, Apple, BCG, Delta, Facebook, Google, Mars, Shopify, Stripe, Swiss Re, United and Velux \cite{Mic21}. Of the aforementioned, Shopify, Stripe and Microsoft are making carbon removal a core focus in their business. More specifically Microsoft has a plan to remove carbon that they emit, and came to key conclusions. Namely, they can not meet current carbon negative commitments and estimate that they need to remove 6 Million Tons of carbon in 2030. Hence, an RFP was sent out in 2020 and 79 applications were received and 15 organizations were selected representing 1.3 Million metric tons of carbon removal. Their project selection process was based on several criteria: (a) Global carbon removal potential; (b) Affordability targeting \$15 per mtCO$_{2}$; (c) climate equity; (d) technology innovation; and (e) other sustainability dimensions.

In 2019, the National Academies of Sciences, Engineering, and Medicine investigated the likely market size for Negative Emissions Technologies (NET), where they discuss how much carbon uptake is needed to meet Paris Agreement goals \cite{NET19}. They estimate that $\sim$ 10 GtCO$_{2}$ / yr is required globally by midcentury and $\sim$ 20 GtCO$_{2}$ / yr globally by centuries end to meet these goals. Six key sequestration technologies are identified which are: (a) coastal carbon blue; (b) terrestrial carbon removal and sequestration; (c) bioenergy with carbon capture and sequestration (BECCS); (d) geological sequestration; (e) direct air capture;  and (f) carbon mineralization. Of these aforementioned technologies, the former four are ready for large-scale deployment; see Table \ref{table:net} for estimated potential rates across US and the Globe.

\begin{table}[h]
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 Negative Emission Technology & Estimated Cost (\$/tCo$_{2}$) &\multicolumn{2}{ c |}{ Upper Bound for Safe Potential rate of CO$_{2}$ (GtCO$_{2}$/y)}  \\
  & & US & Global \\
\hline
Coastal blue carbon & L & 0.02 & 0.13  \\
Afforestation / Reforestation & L & 0.15 & 1  \\
Forest management & L & 0.1 & 1.5  \\
Agricultural soils & L to M & 0.25 & 3  \\
BECCS & M & 0.5 & 3.5-5.2  \\
Direct air capture & H & 0 & 0  \\
Carbon mineralization & M to H & unknown & unknown \\
Total &  & 1.02 & 9.13-10.83 \\
\hline
\end{tabular}
\caption{Estimated potential rates of CO$_{2}$ removal for various Negative Emission Technologies (measured in GtCO$_{2}$ / y) for the US and across the globe (see \cite{NET19} for source), we see BECCS offer the best opportunity.}
\label{table:net}
\end{table}

@@

We propose that token supply creation requires work, which include Carbon sequestration followed by an auditing process working with various stakeholders that are involved in the process. The minting of new token supply can be compared to Bitcoin's Proof-of-Work (PoW) process popularily described an \emph{mining}, which is a completely automated and trustless process. However, the Carbon Renaissance (CR) token minting process will be governed by a regulatory work-flow process working through various stakeholders, which will be covered throughout this whitepaper. Many of the market dynamics that we know which drive price discovery via the Bitcoin miner network can be utilized to understand the market dynamics with this project. Such dynamics include: (a) geographical advantages characteristic to the local environment; (b) regulations particular to certain jurisdictions that allow for more cost effective sequestration; and (c) technological advancements.

The token supply can work in both a inflation/deflation environment depending on the system setup. Whereas other projects are either strictly deflationary or inflationary. For instance, we show via simulation that it is possible to have the supply reach a state of equilibrium where supply is constant.  This economic feature can make it attractive for large corporate organizations and governments to work with.

The CR process works in a cycle where the token can move to one of three different states over time (ie, statetokens). These states are: (a) Green; (b) Red; and (c) Black, and are usecase dependant. Green tokens (ie,  otherwise refereed as base tokens) are purchased on exchanges and represent the potential of what can be utilized for carbon sequestration and are required to enter into the auditing process. Red tokens are non-tradable Non-Fungible Tokens (NFT) and represent unique IOU contracts between stakeholders who have intentions to sequester Carbon and those who offer the carbon sequestration service; see Fig. \ref{fig:red_to_green}. NFTs are unique digital assets that are stored on a blockchain and cannot be exchanged for one another, hence non-fungible. Finally, Black tokens represent sequestered carbon. For instance, 100 Black tokens represent proof of 100 units of sequestered carbon. These tokens are created when either Red or Green tokens are burned. Black tokens can be either held privately or can be publicly purchased on exchanges. Holding these tokens over time have the advantage of generating Green tokens which can generate additional revenue by being sold and recycled back into the system. We will be expounding further into the dynamics and utility behind these statetokens throughout this whitepaper.

\subsubsection{NFT Tokens}
\label{section:nft_tokens}

NFT tokens represent legal contracts and partnership with NFT issuances, see Fig \ref{fig:red_green_issue} for the relationship between these stakeholders. They have the ability to white and black list those issuances to control the conversions, and have the authority to issue monetary redemptions of those NFT’s for when they break contract rules. Bundling these NFTs into these promissory contracts helps decouple concerns between pollution prevention companies and users of the credits. This idea allows stakeholders to seamlessly enable onboarding of partners without upfront costs. This disruptive technology allows for the seamless onboarding of partners without upfront costs and regulatory pressures that would otherwise slow down the workflow process using traditional means. We foresee that not requiring upfront investment and low barrier of entry for existing pollution prevention services will greatly increase the chance of network effects. Participants can target businesses by offering them the NFT and liquidity on the open market in exchange for their services.

There is no responsiveness required on behave of pollution prevention service providers as they can do as little or as much work as they want. Hence, no queues and no required customer acquisitions are required. All provided services are compensated (ie, as long as it's audited and verified) and are motivated to be efficient by decoupling prevention of pollution from customer demand.

NFT tokens are minted upon the creation of each new contract, which is a promissory note to sequester a pre-determined amount of carbon. Once the obligation of NFT contract is fulfilled, Green tokens are issued in exchange for service provided which in turn increase Green token supply. However, overall Green supply increases when NFTs are minted, but not tradable Green tokens themselves. Hence, by definition total Green supply includes the aggregation of tradable Green tokens and non-tradable NFTs. Pre-negotiated rates (even in non-token values if needed) are possible between stakeholders and CR for NFT to Green token exchange. This will give the ability to offload speculative concerns on the sequestration services part to CR. These speculative concerns can also be abated via raising capital to offer liquidity on the markets (ie, to buy Green tokens) when needed as well.

@@

In some systems the proposed UBI solutions are targeted to close the segregation between the rich and poor but come at the cost of political interference. However these systems rarely work in practice because of the lobbying from the wealthy which have power to unilaterally dismiss such systems that intend to close the gap through taxation on rich and profitable corporations (REF). Companies and people that move would ideally be met with similar taxation systems in other jurisdictions however we foresee these other jurisdictions may or may not comply depending on their own policies and mandates to grow local economies through immigration of these wealthy people and companies.

Using our carbon offset token program, governments can purchase carbon offsets, which are an efficient spend of budget against environmental impacts of its economy and reduce taxes to those that inhibit environmentally responsible spending habits (such as buying local and not going over their carbon footprint quota per person). Hence, creating a positive feedback loop to incentivize people to adapt their spending habits is a great way to find new efficiencies and invent \emph{greener} technologies due to increased demand for such technologies and services. The work here will be to assign carbon scores to goods and services and also assign spending against carbon ratings of goods and services. People that have a negative carbon footprint can be paid in Green tokens creating a powerful driver to reduce pollution and assigning monetary benefits which can be a social credit component to a UBI system, one which is tied to actual production and verified work.

@@

In the CR process, tokens move through a series of three states in an acyclic fashion. When the token is in a particular state, it can otherwise be defined as a Statetoken, and (as discussed in the previous section) can take on the characteristics of one of three forms (ie, Green, Red, and Black). Upon initial issuance, 100M Green tokens are issued by CR, and over time this supply is set to decrease, while the supply of Red and Black tokens rise from zero to some steady-state equilibrium over time. Fig \ref{fig:state_diagram} illustrates the state transition diagram where the nodes represent tokens and the arcs represent the direction and probability of a token transitioning to another over a unit of time.

@@

The NFT stays in the possession of the sequesterer until the work has been performed and verified via the auditing process, see Fig \ref{fig:red_to_green}. Once complete, the NFT is burned and exchanged for both Black tokens as proof of sequestration and Green tokens which can be sold for revenue. Further to that, Black tokens can be held by sequesterer which when held over time slowly burn back into Green tokens. Each NFT may have its own rules, regulations and even sequestering costs factoring in base asset to NFT cost ratios.

\begin{figure}[h]
\centering
\includegraphics[width=4in]{red_to_green.png}
\caption{ Process workflow illustrating how Green tokens are minted through the auditing of Red NFT contracts } 
\label{fig:red_to_green}
\end{figure}

Burning Green directly tokens can also result Black tokens directly by entering into the auditing process to apply credit to the pollution prevention stakeholder. Once Green tokens are burned the holder will receive Black tokens. Holding these tokens is advantageous over extended periods of time, which will result in the minting or new Green tokens. For instance, if the state transition probability from Black to Green is 0.01, then 100 Black tokens will produce 1 Green token and 99 Black tokens when the state transitions across one unit of time.

\begin{figure}[h]
\centering
\includegraphics[width=4in]{green_to_black.png}
\caption{ Process workflow illustrating how Green tokens are burned to mint Black tokens } 
\label{fig:green_to_black}
\end{figure}

Green token supply increases as sequestering happens and decreases as companies accumulate and burn Green tokens as proof that they have credits. If the rate of seqestration exceeds the rate of credit consumed by companies ,then the Green token supply is inflationary and is deflationary if sequestering doesn’t adequately satisfy the burning of credits to black. For the deflationaray case, sequestering services will naturally start to fill the demand and organically find equilibrium.

@@

It was requested that we create a fungible token for the purpose of share allocations in a company represented as a token product on blockchain. Also, these shares should not be transferable unless explicitly allowed by CR. We can enable this functionality on Syscoin through Notary services which will allow a case-by-case basis for transaction authorization between peer-to-peer (P2P) transfers. Here are the following token specifications:

Token to sell to raise funds
\begin{itemize}
\item \textbf{Max supply}: 100m
\item \textbf{Precision}: 8
\item \textbf{Total raise}: sell 10m upfront @ \$10
\item \textbf{Token symbol}: GCX
\end{itemize}

@@

\subsection{Tokenomics}
\label{section:token_model}

>>>>

 \href{https://orcid.org/0000-0000-0000-0000}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Greg Darragh}\\
	Carbon Renaissance\\
	\texttt{greg@crc.eco} \\
\And	
 \href{https://orcid.org/0000-0000-0000-0000}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}M J Viner Smith}\\
	Carbon Renaissance\\
	\texttt{mick@crc.eco} \\

	\And
	\href{https://orcid.org/0000-0000-0000-0000}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Jagdeep Sidhu, MSc} \\
	Blockchain Foundry Inc.\\
	\texttt{jsidhu@blockchainfoundry.co} \\
\And
 \href{https://orcid.org/0000-0000-0000-0000}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm} Ahmad Sghaieromar Omar, PhD}\\
	Blockchain Foundry Inc.\\
	\texttt{asghaier@blockchainfoundry.co} \\	
\And
 \href{https://orcid.org/0000-0000-0000-0000}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Ian C. Moore, PhD}\\
	Syscoin Platform\\
	\texttt{imoore@syscoin.org} \\		
}

@@

@@

We introduce a carbon offsetting program through the tokenization of the performed sequestration work (ie, via Green tokens) on a blockchain. We utilize non-fungible tokens as IOU contracts to facilitate engagement between stakeholders interested in pollution prevention and those performing the carbon offsetting. To incentivize adoption, a Black reward token is offered for those who utilize the system, which can be staked to acquire Green tokens introduced to the supply

@@

\keywords{Carbon Markets \and Carbon Offsetting \and Climate Change  \and Blockchain \and NFT \and Social Credit}

@@

We propose a carbon offset design that creates natural economic incentives through business
processes on the blockchain tied to non-fungible tokens (NFT) tokens issued from enterprise to participating companies which connect to the carbon offsetting processes. Upon audits of work, a fungible token (ie, Green token) is issued to companies involved based on a pre-negotiated ratio of tokens dispersed based on the quality of the work and quality of the credit-worthiness of the companies involved. Green tokens represent auditing work done for carbon offsetting.

We conjecture that this will not only allow for incentives to modify spending behaviour of
consumers, but also produce a mechanism for stakeholders to adhere to carbon quotas by
purchasing and offsetting their carbon consumption through a novel token model. Furthermore, once our model is implemented for fair exchange of carbon tokens in auditable and censorship resistance mediums, we assert how this model can be used to serve as a social credit component to a broader Universal Basic Income (UBI) model.

@@

Climate change is a well studied issue and is defined as global warming stemming from greenhouse gas emissions resulting from major shifts in weather patterns. As a result, it has garnered much attention on the world stage \cite{Kal96,Ten00,Hij05}. According to \cite{Glo21}, it is estimated that human activity accounts for 1.0 $^\circ$C of global warming above pre-industrial levels, and estimate that global warming is likely to reach 1.5$^\circ$C between 2030 and 2052. The EDGAR time series set shows that since the beginning of the 21$^{st}$ century \cite{EDGAR19}, fossil CO$_{2}$ emissions have increased compared to the three previous decades (see Fig \ref{fig:edgars_co2_emissions}). It also shows that, as of 2018, global fossil CO$_{2}$ emissions have reached a total of 37.9 Gt CO$_{2}$. However, according to \cite{Liu20}, emissions have fallen \~ 1,900 MtCO$_{2}$ from 2019 to 2020 due mainly to the aviation and shipping sector due to the slowing of economic activity stemming from the 2020 pandemic. To combat this, carbon offsetting is the process by which many institutions are handling this issue.

\begin{figure}[h]
\centering
\includegraphics[width=5in]{edgars_co2_emissions.png}
\caption{Global Greenhouse Gas (GHG) emission per sector (see \cite{EDGAR19}). We see that the Power industry accounts for a large portion of global emissions, which provides insight as to where the largest opportunity for carbon reduction may be found.} 
\label{fig:edgars_co2_emissions}
\end{figure}

Carbon offsetting is done via sequestration, which is the process where atmospheric carbon dioxide is captured and stored for the purpose of abating climate change. After carbon is captured, it goes mainly one of two ways: (a) permanently stored underground; or (b) converted into a carbon-containing product \cite{CBC19}. Currently, the market for corporate procurement for carbon removal is very undeveloped. However, there are a number of organizations that have made strides to address this issue; which include Amazon, Apple, BCG, Delta, Facebook, Google, Mars, Shopify, Stripe, Swiss Re, United and Velux \cite{Mic21}. Of the aforementioned, Shopify, Stripe and Microsoft are making carbon removal a core focus in their business. More specifically, Microsoft has a plan to remove carbon that they emit, and came to key conclusions. Namely, they can not meet current carbon negative commitments and estimate that they need to remove 6 Million tons of carbon in 2030. Hence, an RFP was sent out in 2020 and 79 applications were received and 15 organizations were selected representing 1.3 Million metric tons of carbon removal. Their project selection process was based on several criteria: (a) Global carbon removal potential; (b) Affordability targeting \$15 per MtCO$_{2}$; (c) climate equity; (d) technology innovation; and (e) other sustainability dimensions.

In 2019, the National Academies of Sciences, Engineering, and Medicine investigated the likely market size for Negative Emissions Technologies (NET), where they discussed how much carbon uptake is needed to meet Paris Agreement goals \cite{NET19}. They estimate that $\sim$ 10 GtCO$_{2}$ / yr is required globally by midcentury and $\sim$ 20 GtCO$_{2}$ / yr globally by centuries end to meet these goals. Six key sequestration technologies are identified which are: (a) coastal carbon blue; (b) terrestrial carbon removal and sequestration; (c) bioenergy with carbon capture and sequestration (BECCS); (d) geological sequestration; (e) direct air capture;  and (f) carbon mineralization. Of these aforementioned technologies, the former four are ready for large-scale deployment; see Table \ref{table:net} for estimated potential rates across US and the Globe.

\begin{table}[h]
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 Negative Emission Technology & Estimated Cost (\$/tCo$_{2}$) &\multicolumn{2}{ c |}{ Upper Bound for Safe Potential rate of CO$_{2}$ (GtCO$_{2}$/y)}  \\
  & & US & Global \\
\hline
Coastal blue carbon & L & 0.02 & 0.13  \\
Afforestation / Reforestation & L & 0.15 & 1  \\
Forest management & L & 0.1 & 1.5  \\
Agricultural soils & L to M & 0.25 & 3  \\
BECCS & M & 0.5 & 3.5-5.2  \\
Direct air capture & H & 0 & 0  \\
Carbon mineralization & M to H & unknown & unknown \\
Total &  & 1.02 & 9.13-10.83 \\
\hline
\end{tabular}
\caption{Estimated potential rates of CO$_{2}$ removal for various Negative Emission Technologies (measured in GtCO$_{2}$ / yr) for the US and across the globe (see \cite{NET19}), in terms of abundance, we see BECCS offers the best opportunity.}
\label{table:net}
\end{table}

@@

We propose that token supply creation requires work, which include carbon sequestration followed by an auditing process working with various stakeholders involved in the process. The minting of new token supply can be compared to Bitcoin's Proof-of-Work (PoW) process popularly described as \emph{mining}, which is a completely automated and trustless process. However, the Carbon Renaissance (CR) token minting process will be governed by a regulatory work-flow process working through various stakeholders, which will be covered in this whitepaper. Many of the market dynamics that we know which drive price discovery via the Bitcoin miner network can be utilized to understand the market dynamics with this project. Such dynamics include: (a) geographical advantages characteristic to the local environment; (b) regulations particular to certain jurisdictions that allow for more cost effective sequestration; and (c) technological advancements.

The token supply can work in both an inflation/deflation environment depending on the system setup. Whereas other projects are either strictly deflationary or inflationary. For instance, we show via simulation that it is possible to have the supply reach a state of equilibrium where supply is constant.  This economic feature can make it attractive for large corporate organizations and governments to work with.

The CR process works in a cycle where the token can move to one of three different states over time (ie, statetokens). These states are: (a) Green; (b) Red; and (c) Black, each of which are usecase dependant. Green tokens (ie,  otherwise refereed to as base tokens) are purchased on exchanges and represent the potential of what can be utilized for carbon sequestration and are required to enter into the auditing process. Red tokens are non-tradable non-fungible tokens (NFT) and represent unique IOU contracts between stakeholders who have intentions to sequester carbon and those who offer the carbon sequestration service (see Fig. \ref{fig:red_to_green}). NFTs are unique digital assets that are stored on a blockchain and cannot be exchanged for one another, hence non-fungible. Some other example uses of NFTs are: (a) gaming; (b) digital art; (c) physical assets; and (d) digital collectibles.  Finally, Black tokens represent sequestered carbon. For instance, 100 Black tokens represent proof of 100 units of sequestered carbon and are created when Green tokens are burned. Black tokens are held privately and holding these tokens over time have the advantage of generating Green tokens which can generate additional revenue by being sold and recycled back into the system. We will be expounding further into the dynamics and utility behind these statetokens throughout this whitepaper.

\subsubsection{NFT Contracts}
\label{section:nft_tokens}

NFT contracts represent a legal framework and partnership with NFT issuances, see Fig. \ref{fig:red_green_issue} for the relationship between these stakeholders. They have the ability to white and black list those issuances to control the conversions, and have the authority to issue monetary redemptions of those NFT’s for when they break contract rules. Bundling these NFTs into these promissory contracts helps decouple concerns between pollution prevention companies and users of the credits. This idea allows stakeholders to seamlessly enable onboarding of partners without upfront costs. This disruptive technology allows for the seamless onboarding of partners without upfront costs and regulatory pressures that would otherwise slow down the workflow process using traditional means. We foresee that not requiring upfront investment and low barrier of entry for existing pollution prevention services will greatly increase the chance of network effects. Participants can target businesses by offering them the NFT and liquidity on the open market in exchange for their services.

There is no responsiveness required on behalf of pollution prevention service providers as they can do as little or as much work as they want. Hence, no queues and no required customer acquisitions are required. All provided services are compensated (ie, provided they are audited and verified) and are motivated to be efficient by decoupling prevention of pollution from customer demand.

NFT tokens are minted upon the creation of each new contract, which is a promissory note to sequester a pre-determined amount of carbon. Once the obligation of the NFT contract is fulfilled, Green tokens are issued to the sequestration provider in exchange for service provided which in turn increases Green token supply. It should be noted that overall Green supply increases when NFTs are minted, but not tradable themselves until the contract is fulfilled. Hence, by definition total Green supply includes the aggregation of tradable Green tokens and non-tradable NFTs. Once fulfilled, these newly minted Green tokens are then bought by the pollution prevention company to meet their end of the contractual obligation laid out by the NFT. Pre-negotiated rates (even in non-token values if needed) are possible between stakeholders and CR for NFT-to-Green token exchange. This will give the ability to offload speculative concerns on the sequestration services part to CR. These speculative concerns can also be abated via raising capital to offer liquidity on the markets when needed as well.

@@

In some systems, the proposed UBI solutions are targeted to close the segregation between the rich and poor, but come at the cost of political interference. However these systems rarely work in practice because of the lobbying from the wealthy which have power to unilaterally dismiss such systems that intend to close the gap through taxation on rich and profitable corporations. Companies and people that move would ideally be met with similar taxation systems in other jurisdictions, however we foresee these other jurisdictions may or may not comply depending on their own policies and mandates to grow local economies through immigration of these wealthy people and companies.

Using the proposed carbon offset token program, governments can purchase carbon offsets, which can be considered as an efficient budget spending against environmental impacts of its economy and reduce taxes to those that inhibit environmentally responsible spending habits (such as buying local and not exceeding their carbon footprint quotas). Hence, creating a positive feedback loop to incentivize people to adapt their spending habits is a great way to find new efficiencies and invent \emph{greener} technologies due to increased demand for such technologies and services. The work here will be to assign carbon scores to goods and services and also assign spending against carbon ratings of goods and services. People that have a negative carbon footprint can be paid in Green tokens creating a powerful driver to reduce pollution and assigning monetary benefits which can be a social credit component to a UBI system, one which is tied to actual production and verified work.

@@

In the CR process, tokens move through a series of three states in an cyclic fashion. When the token is in a particular state, it can otherwise be defined as a statetoken, and (as discussed in the previous section) can take on the characteristics of one of three forms (ie, Green, Red, and Black). Upon initial issuance, 100M Green tokens are issued by CR, and over time this supply is set to decrease, while the supply of Red and Black tokens rise from zero to some steady-state equilibrium. Fig. \ref{fig:state_diagram} illustrates the state transition diagram where the nodes represent tokens and the arcs represent the direction and probability of a token transitioning to another over a unit of time.

@@

The NFT stays in the possession of the sequesterer until the work has been performed and verified via the auditing process (see Fig. \ref{fig:red_to_green}). Once complete, the NFT is burned and exchanged for Green tokens which is sold back to the pollution prevention company for revenue. Each NFT may have its own rules, regulations and even sequestering costs factoring in base asset to NFT cost ratios.

\begin{figure}[h]
\centering
\includegraphics[width=4in]{red_to_green.png}
\caption{Process workflow illustrating how Green tokens are minted through the auditing of Red NFT contracts } 
\label{fig:red_to_green}
\end{figure}

Burning Green tokens directly result in Black tokens directly by entering into the auditing process to apply credit to the pollution prevention stakeholder; see Fig. \ref{fig:green_to_black}. Once Green tokens are burned the holder will receive Black tokens. Holding these tokens is advantageous over extended periods of time, which will result in the minting of new Green tokens. For instance, if the state transition probability from Black to Green is 1\%, then 100 Black tokens will produce 1 Green token and 99 Black tokens when the state transitions across one monthly time unit.

\begin{figure}[h]
\centering
\includegraphics[width=4in]{green_to_black.png}
\caption{Process workflow illustrating how Green tokens are burned to mint Black tokens} 
\label{fig:green_to_black}
\end{figure}

Green token supply increases as sequestering happens and decreases as companies accumulate and burn Green tokens as proof that they have credits. If the rate of sequestration exceeds the rate of credit consumed by companies, then the Green token supply is inflationary and is deflationary if sequestering does not adequately satisfy the burning of credits to black. For the deflationary case, sequestering services will naturally start to fill the demand and organically find equilibrium.

@@

It was requested that we create a fungible token for the purpose of share allocations in a company represented as a token product on blockchain. Also, these shares should not be transferable unless explicitly allowed by CR. We can enable this functionality on Syscoin through notary services which will allow a case-by-case basis for transaction authorization between peer-to-peer (P2P) transfers. Here are the following token specifications:

Token to sell to raise funds
\begin{itemize}
\item \textbf{Max supply}: 100M
\item \textbf{Precision}: 8
\item \textbf{Total raise}: sell 10M upfront @ \$34 US
\item \textbf{Token symbol}: GCX
\end{itemize}

@@

\subsection{Supply Tokenomics}
\label{section:token_model}

Due to the nature of the supply dynamics involved with how each of the three tokens interact with each other, we have chosen to apply a Markov Chain simulation model to get a better understanding of what to expect under different conditions. For our problem, we setup the following transition matrix representing our business targets, where the frequency is monthly, and the states are represented as Green, NFT, and Burned respectively. To get an understanding of the underlying technicals, please refer to Appendix \ref{section:tokenomics}.

\begin{table}[h!]
\centering
\begin{tabular}{|c c|c|c|c| } 
\hline
 & \multicolumn{4}{ c |}{ Next State } \\
 &  & Green & NFT & Burned \\
\hline
\multirow{ 3}{*}{Current State} & Green &  85\% & 0 & 15\% \\
& NFT & 33\% & 67\% & 0\\
& Burned & 1\% & 0 & 99\% \\
\hline
\end{tabular}
\caption{Transition state matrix for token model detailing probabilities of transitioning from current to next state over a monthly unit of time.}
\label{table:trans_state_matrix}
\end{table}

See Table \ref{table:trans_state_matrix} for the state transition matrix which represents our chosen business targets on how we believe the system will behave over time. For instance, for some stakeholder holding Green tokens, we are targeting 95\% of those tokens will remain in the hands of the holder at the next monthly time increment, and 5\% of those tokens will get burned into Black tokens. Since there is no current business case for a Green token to transition to a Red token, there is a 0\% chance that Green will transition to a Red token. With regards to NFTs, we are anticipating contract lengths to run 3 months on average. Hence, if a stakeholder runs back-to-back contracts over the course of a year, there is a 67\% chance that the holder will be holding their contract on any given month when they transition to the next month, and a 33\% chance that it will get burned. Finally, regarding Black tokens, since they represent proof of burn, we have decided to include an incentive for users that hold them, as a loyalty for users of the system so that they stay enticed to continue to stay engaged with the network. If a stakeholder is holding Black tokens, then 1\% of them will get converted back to Green at the next monthly time increment, which can then be reintegrated back into the cycle or sold back into the market. See Fig. \ref{fig:token_supply_sims} for simulation using methodology outlined in Appendix \ref{section:tokenomics} and Fig. \ref{fig:burned_minted} for simulated number of newly minted Green and Black tokens.

\begin{figure}
\centering
\includegraphics[width=4in]{token_supply_sims.png}
\caption{Markov Chain Token (MCT) model simulations assuming stationary transition probabilities applying the Beta distribution at each time point at a monthly frequency. The expectations of the transition probability matrix (\ref{e:transition_matrix}) was selected based on business targets. The simulation begins with 100M Green tokens, the bulk of which will transition to red and black tokens over time and eventually reach a state of equilibrium. When the system reaches steady-state, the expected supply of each of the Green tokens will become relatively stable with a slow increasing uptick over time.} 
\label{fig:token_supply_sims}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=4in]{burned_tokens.png}
\caption{Plot of simulated sequestered tons of carbon; this is determined by taking the cumulative sum of generated Black tokens overtime } 
\label{fig:burned_tokens}
\end{figure}

Both Green and Black tokens are fungible hence tradable on exchanges, but serve different ways to generate revenue. Green tokens are earned from sequestering carbon (ie, through NFT to Green token conversions) which can be sold for profit. Black tokens are earned through burning NFT or Green tokens. These Black tokens can be held privately which burn slowly over time (ie, at a predetermined rate set by CR) producing Green tokens that can be sold for profit or utilized back into the system. Aside from the tokens themselves, value added services such as software and wallets are other revenue generating options that companies may pay services for.

Here, we approximate annual revenue (ie, first five years) based on simulated tonnes of sequestered carbon and estimated price of carbon; see Fig. \ref{fig:burned_tokens}. These estimated revenue figures are a back of the envelope calculation as we did not have any long term historical carbon price data. Thus, we use this as an exercise to get an idea of expected annual revenue generation. We use median carbon tax prices for 2021 as shown in Fig. \ref{figure:nation_carbon_taxes} as a proxy to the price of carbon. To determine the annual growth rate we applied the scheduled 2030 carbon tax price target of \$170 US from Canada's HEHE plan as a proxy. Considering that Canada's 2021 carbon tax price is $\sim$ \$32 US, that would work out to an annual growth rate of $\sim$ 20.5\%; see Table \ref{table:sim_revenue} for annual estimates and revenue projections.

\begin{table}[h]
\centering
\begin{tabular}{ |c|c|c|c|c|c| } 
\hline
 Year & median (tonnes) & lwr 5\% & upr 95\% & est. median price (USD)  & median revenue (USD)  \\
\hline
2023 & 9,056,000 & 8,470,000 & 9,789,000 & \$40.83 & \$369,792,000 \\
2024 & 12,315,000 & 11,959,000 & 12,619,000  & \$49.19 & \$605,749,000 \\
2025 & 14,963,000 & 14,443,000 & 15,448,000 & \$59.25 & \$865,887,000  \\
2026 & 17,620,000 & 17,284,000 & 17,836,000  & \$71.38 & \$1,257,642,000 \\
2027 & 20,293,000 & 19,994,000 & 20,690,000 & \$85.98 & \$1,744,829,000 \\
\hline
\end{tabular}
\caption{Simulated sequestered tons of carbon assuming transition matrix (see Table \ref{table:trans_state_matrix}) as business targets and corresponding median revenue. Since long-term historical market data is not available, we used Canada's current and future schedule 2030 carbon tax prices as a proxy to estimate annual growth rate \cite{Mck21}. Hence, we note that price estimates (ie, 5$^{th}$ column) are not based on rigorous mathematical analysis, but meant to provide an idea of revenue potential for strategic planning purposes.}
\label{table:sim_revenue}
\end{table}

\subsection{Implementation}
